\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
WIP design -- timelines

\subsection{Worlds}

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.
As a result, a \uwds network can be seen as a dependency graph between worlds (where
cyclic dependencies are permissible).

This architecture enables what we call \emph{cascading situation assessment}:
a set of independent software components (the clients) builds and refines
successive models of the environment by a combination of
filtering/transformations steps and model branching.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{timeline}
    \caption{Both events and episodes are stored in the world's \emph{timeline}}

    \label{fig|timeline}
\end{figure}

@@

The cross-platform/cross-language support of gRPC is especially welcomed in the
academic context, as it offers ease and flexibility to plug a variety of
pre-existing components into a \uwds network.

>>>>

\subsubsection{Worlds}

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.
As a result, an \uwds network can be seen as a dependency graph between worlds (where
cyclic dependencies are permissible).

This architecture enables what we call \emph{cascading situation assessment}:
independent software components (the clients) build, refine and share successive
models of the environment by a combination of filtering/transformations steps
and model branching.

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also store the world's \emph{timeline}. This data structure is shared
and synchronized amongst the clients in the same way as the scene graph.
Client can record in the timeline both \emph{events} (duration-less state) and
\emph{situations}, \ie states with a start time and a (possibly open-ended) end time.

Importantly, the \uwds server automatically generates a snapshot of
the scene graph whenever an event or situation is added to the timeline. The
snapshot is associated to the event, which allows clients to effectively retrieve past
states of the world. This capability is thought to be primarly used by \uwds clients
performing action recognition.

@@

The cross-platform/cross-language support of gRPC is especially welcomed in the
academic context, as it offers ease and flexibility to plug a variety of
pre-existing components into an \uwds network.
